Experiment 1 of 4

### 2016-09-25 experiments/e1/writeup/e1.Rmd
changed number of digits in some tables

```{r pander, echo=FALSE}
library(pander)
```

```{r showInstructions, echo = FALSE}
v = c("crisp","vague")
e <- c("Choose the the square with many dots", "Choose the square with 20 dots")
i = data.frame(v, e)
names(i) = c("vagueness", "example instruction")
pander(i, justify=c('center', 'left'))
```

```{r showItems, echo=FALSE}
items = c(1,2,3,4,5,6,7,8)
i = data.frame(Gap = c("05","10","15","20"),
               x = c("25:20","25:15","25:10","25:05"),
               z = c("25:30","25:35","25:40","25:45") )
names(i) = c('Gap Size', 'Small Target', 'Large Target')
pander(i, justify=c('center', 'center', 'center'))
```

```{r loadLibraries, message=FALSE, echo = FALSE}
library(knitr); library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); source('summarySEwithin2.R') 
```

@@

```{r separateDataFramesForRTandErrorAnalyses, echo=T}
rawdata <- read.table('data.txt', sep=' ')
rtdata <- subset(rawdata, error==FALSE)
erdata <- rawdata
```

@@

for (i in ncol(x)) {
  for (j in 1:nrow(x)) {
    x[j,i] <-  substr(x[j,i], start=1, stop=7)
  }
}
print(
  xtable(
    align='lrrrrr', 
    digits=c(0,  2,2,2,2,3),
    x,
    caption="Response time model"), 
    caption.placement="top", 
  type='html')
```

@@

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(summary(
    ac.lmer.1)$coefficients,
         digits=3, 
         caption="Error rates model"),
         caption.placement="top", type='html')
```

>>>>

```{r pander, echo=FALSE, cache=FALSE}
library(pander)
library(knitr)
```

```{r showInstructions, echo=FALSE, cache=TRUE}
v = c("crisp","vague")
e <- c("Choose the the square with many dots", "Choose the square with 20 dots")
i = data.frame(v, e)
names(i) = c("vagueness", "example instruction")
pander(i, justify=c('center', 'left'))
```

```{r showItems, echo=FALSE, cache=TRUE}
items = c(1,2,3,4,5,6,7,8)
i = data.frame(Gap = c("05","10","15","20"),
               x = c("25:20","25:15","25:10","25:05"),
               z = c("25:30","25:35","25:40","25:45") )
names(i) = c('Gap Size', 'Small Target', 'Large Target')
pander(i, justify=c('center', 'center', 'center'))
```

```{r loadLibraries, message=FALSE, echo=FALSE, cache=FALSE}
library(knitr); library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions); source('summarySEwithin2.R') 
```

@@

```{r separateDataFramesForRTandErrorAnalyses, echo=TRUE, cache=FALSE}
rawdata <- read.table('data.txt', sep=' ')
rtdata <- subset(rawdata, error==FALSE)
erdata <- rawdata
```

Correct responses were trimmed at 2.5 sd separately for each subject:

```{r trimData, echo=TRUE, cache=FALSE}
tempdata <- perSubjectTrim.fnc(rtdata, response='rt', subject='subject', trim = 2.5)$data
rtdata <- tempdata
```

@@

for (i in ncol(x)) {
  for (j in 1:nrow(x)) {
    x[j,i] <-  substr(x[j,i], start=1, stop=7)
  }
}
print(
  xtable(
    align='lrrrrr', 
    digits=c(0, 2, 2, 1, 1, 3),
    x,
    caption="Response time model"), 
    caption.placement="top", 
  type='html')
```

@@

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(
    summary(
    ac.lmer.1
    )$coefficients,
    digits=c(0, 2, 2, 2, 5), 
    caption="Error rates model"),
  caption.placement="top", type='html')
```
